Lifting CDCL to Relational Domains

### 2016-10-15 learning.tex
abstract unit rule

For our example, there exists multiple incomaparable reasons for conflict,
marked as {\em cut0, cut1}, in figure~\ref{conflict}.  Here, cut0 is the first UIP.  
Choosing cut0 yields a learnt clause 
$L_0: (x+y<15 \vee -x-y<-15 \vee -x+y<5 \vee x-y<-5 \vee y-10<0 \vee -y+10<0)$.  
A learnt clause $\mathcal{L}$ is obtained by negating the reason for conflict.   
\rmcmt{shall we call learnt clause or learnt transformer ?}
%
\begin{figure}
%\caption{An example of Octagon}\label{octagon}
\scalebox{.65}{\import{figures/}{conflict_graph.pspdftex}}
\label{conflict}
\end{figure} 
%    
\paragraph {\em Backjumping:}
A backjumping procedure undo all the assignments in the trail up to 
a decision level that restores the solver to a consistent state 
(non-conflicting).  The backjumping level is defined by the literal 
of the conflict clause that is closest to the root (decision level 0) 
where the conflict clause is still unit. If a conflict clause is 
globally unit, then the backjumping level is the root of the search tree.

>>>>

For our example, there exists multiple incomaparable reasons for conflict,
marked as {\em cut0, cut1}, in figure~\ref{conflict}.  Here, cut0 is the first UIP.  
Choosing cut0 yields a learnt clause 
$L_0: (x+y<15 \vee -x-y<-15 \vee -x+y<5 \vee x-y<-5 \vee y-10<0 \vee -y+10<0)$.  
%
\begin{figure}
%\caption{An example of Octagon}\label{octagon}
\scalebox{.65}{\import{figures/}{conflict_graph.pspdftex}}
\label{conflict}
\end{figure} 
%    
\paragraph{\textbf{Clause Learning in Abstract Lattice}}
A learnt clause $\mathcal{L}$ in propositional solver is obtained 
by negating the reason for conflict.  An asserting clause guarantees 
new dductions using unit rule~\cite{cdcl}.  However, we model a 
learnt clause as abstract deduction transformer, called {\em abstract unit 
transformer (AUnit)}.  For an abstract lattice $A$ and a set of 
countermodels $C \subseteq A$ of $\varphi$ such that \meet{C} does not 
satisfy $\varphi$, $AUnit_C: A \rightarrow A$ is $\top$ if $\exists a \in A$ 
such that $a \subseteq \meet{C}$.  However, if $t \in C$ and 
$\forall t' \in C \ {t}$ such that $a \sqsubseteq t'$, $AUnit$ 
infers a valid deduction $\bar{t}$, which directs the search 
away from the conflict region. Else, $AUnit$ returns $\top$.

\paragraph {\textbf{Backjumping}}
A backjumping procedure undo all the assignments in the trail up to 
a decision level that restores the solver to a consistent state 
(non-conflicting).  The backjumping level is defined by the literal 
of the conflict clause that is closest to the root (decision level 0) 
where the conflict clause is still unit. If a conflict clause is 
globally unit, then the backjumping level is the root of the search tree.
